HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-12 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex

	\textbf{Author response:} We thank the referee for this remark. One of the novelties of the proposed approach is that we present a general hybrid framework able to include all univariate models and it is why we only introduced a general notation $f^n()$ in Section 3 for this model. In the paper we propose different models: exponential smoothing, Thetam and TBATS. These models are given with the references as they are not the contribution of the paper, but could be added in the appendix if necessary.

We acknowledge that this feature of the proposed model was not sufficiently highlighted in the original paper. Consequently, additional information has been added in Section 3 and a third HERMES variation has been added in Section 4 to illustrate this point.\\

	\item {\em ``The term "error correction" sounds misleading as there is not such an explicit algorithm to compute the error. Perhaps the second term of (3) should be called just the correction term. ''} \medskip

	\textbf{Author response:} We thank the referee for these remarks and the text has been corrected accordingly.\\

### 2023-07-20 tmlr_submission/hermes_paper_revision/answers_reviewer_4.tex

	\textbf{Author response:} We thank the referee for these remarks and the text has been corrected accordingly.\\

	\item {\em ``I need methodological validation on (4). Apparently, the scaling of the input of RNN is critical to serving the RNN term as the coefficient of the correction term.''} \medskip

	\textbf{Author response:} The 10000 time series in the fashion dataset have different volumes, from $10^{-5}$ for niche trends to $10^{-1}$ for common trends. As we want to train the RNN part on the whole dataset to learn cross dynamics, the normalization step of the RNN input is inevitable. Two methods have been tested and are discussed at the end of Section 3.2. i) The RNN input can be normalized by directly dividing it by the prediction of the univariate model prediction. ii) The RNN input can be normalized by the mean volume of the time series. The first solution presents a main issue that it shows instabilities with time series close to 0 and it can simply not be used if the prediction of the univariate model prediction hits 0. Consequently, the second solution is used in the proposed hybrid framework.

Of course, other scaling procedures could be used. In this paper this is not the main topic of interest and this step is used to design a training procedure that can deal with thousands of time series. Analyzing in detail the impact of the scaling procedure on the overall training is left for future works.\\

	\item {\em ``I understand the review was delayed. My comment is based on the original submission. If the data preprocessing is a sort of heuristic chosen in an ad hoc manner (that's perfectly fine, if you are not claiming technical contributions there), you may want to mention it clearly to avoid confusion.''} \medskip

	\textbf{Author response: We agree with the referee and the  the text has been corrected accordingly.}

\end{itemize}
\end{document}

### 2023-07-20 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add modif linked to the second answer of the 4th reviewer

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias. Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $\textcolor{orange}{j}$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,\textcolor{orange}{j}}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}

>>>>

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,\textcolor{orange}{j}}$ in order to remove bias. \textcolor{orange}{The pre-processing of data presented in this section does not constitute a technical contribution. We present this step in depth to clearly explain how fashion time series are constructed.} Let $\Tilde{y}^{c,g,m}$ be the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $\textcolor{orange}{j}$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,\textcolor{orange}{j}}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}
